### 2015-12-11 PrincipiaMetaphysicaAutomationPart1/doc/document/TheoryOfAbstractObjectsV1.tex
further improvements: syntax, binder modified definition of identity relations

 The motivating research questions for the work presented below include:
 \begin{itemize} 
 \item Can functional type theory, despite the problems as pointed by Zalta and Oppenheimer, 
  be utilized to encode the Theory of Abstract Objects when following the embeddings approach?
 \item How elegant and user-friendly is the resulting formalization? In other
  words, to what extend can Isabelle's  user interface be facilitated to hide 
  unpleasant technicalities of the (extended) embedding from the user?
 \item How far can automation be pushed in the approach? How much user interaction can
  be avoided in the formalization of the (first part) of the Principia Metaphysica? 
 \item Can the consistency of the theory be validated with the available automated 
  reasoning tools?
 \item Can the reasoners eventually even contribute some new knowledge? 
 \ldots
 \end{itemize}%
\end{isamarkuptext}%
\isamarkuptrue%
%
\begin{isamarkuptext}%
The encoding of modal functional type theory in functional type theory as explored in 
 previous work \cite{J23,C40} is simple: modal logic formulas are identified with certain functional 
 type theory formulas of predicate type \isa{io}. Possible worlds are explicitly represented by 
 terms of type  \isa{i}. A modal logic \isa{{\isasymphi}} formula holds for a world \isa{w} if and 
 only if the application \isa{{\isasymphi}\ w} evaluates to true. The definition of the propositional modal logic 
 connectives is then straightforward and it simply realizes the standard translation as a set of equations 
 in functional type theory. The approach has been successfully extended for quantifiers. A crucial 
 aspect thereby is that in simple type theory quantifiers can be treated
 as ordinary logical connectives. No extra binding mechanism is needed since the already existing 
 lambda binding mechanism can be elegantly utilized.

 The challenge in this work is to appropriately 'restrict' this embedding for modal relational type theory.
  \begin{figure}[t]
 \includegraphics[height=5.5cm]{ModalRelationalTypeTheory.png}\includegraphics[height=4.5cm]{ModalRelationalTypeTheory2.png}
 \caption{Grammar of Modal Relational Type Theory. \label{mmrt}
 Note that two kinds of (complex) formulas are introduced: ones that may have encoding subformulas and ones that don’t.
 The latter are designated as propositional formulas, the former ones simply as formulas. }
 \end{figure}

@@

 Our formalism explicitly encodes Kripke style semantics. Hence, we introduce a 

@@

 datatype \isa{{\isacharprime}a\ opt} based on four constructors:
 \isa{ERR\ {\isacharprime}a} (identifies erroneous term constructions), \isa{P\ {\isacharprime}a} (identifies 

@@

\ mkP{\isacharcolon}{\isacharcolon}{\isachardoublequoteopen}io{\isasymRightarrow}io\ opt{\isachardoublequoteclose}\ {\isacharparenleft}{\isachardoublequoteopen}{\isacharunderscore}\isactrlsup P{\isachardoublequoteclose}\ {\isadigit{1}}{\isadigit{1}}{\isadigit{0}}{\isacharparenright}\ \ \isakeyword{where}\ {\isachardoublequoteopen}{\isasymphi}\isactrlsup P\ {\isasymequiv}\ P\ {\isasymphi}{\isachardoublequoteclose}\ \isanewline
\ mkF{\isacharcolon}{\isacharcolon}{\isachardoublequoteopen}io{\isasymRightarrow}io\ opt{\isachardoublequoteclose}\ {\isacharparenleft}{\isachardoublequoteopen}{\isacharunderscore}\isactrlsup F{\isachardoublequoteclose}\ {\isadigit{1}}{\isadigit{1}}{\isadigit{0}}{\isacharparenright}\ \ \isakeyword{where}\ {\isachardoublequoteopen}{\isasymphi}\isactrlsup F\ {\isasymequiv}\ F\ {\isasymphi}{\isachardoublequoteclose}\ \isanewline
\ mkT{\isacharcolon}{\isacharcolon}{\isachardoublequoteopen}{\isacharprime}a{\isasymRightarrow}{\isacharprime}a\ opt{\isachardoublequoteclose}\ {\isacharparenleft}{\isachardoublequoteopen}{\isacharunderscore}\isactrlsup T{\isachardoublequoteclose}\ {\isadigit{1}}{\isadigit{1}}{\isadigit{0}}{\isacharparenright}\ \ \isakeyword{where}\ {\isachardoublequoteopen}{\isasymphi}\isactrlsup T\ {\isasymequiv}\ T\ {\isasymphi}{\isachardoublequoteclose}\isanewline
\ mkE{\isacharcolon}{\isacharcolon}{\isachardoublequoteopen}{\isacharprime}a{\isasymRightarrow}{\isacharprime}a\ opt{\isachardoublequoteclose}\ {\isacharparenleft}{\isachardoublequoteopen}{\isacharunderscore}\isactrlsup E{\isachardoublequoteclose}\ {\isadigit{1}}{\isadigit{1}}{\isadigit{0}}{\isacharparenright}\ \ \isakeyword{where}\ {\isachardoublequoteopen}{\isasymphi}\isactrlsup E\ {\isasymequiv}\ ERR\ {\isasymphi}{\isachardoublequoteclose}%

@@

 \isa{E} (error) or \isa{T} (term), then the syntactical catagory of \isa{{\isasymA}\ {\isasymphi}} 
 is \isa{E} and a dummy entity of appropriate type is returned. This illustrates the very 

@@

 Encoding \isa{{\isasymkappa}\isactrlsub {\isadigit{1}}{\isasymPi}\isactrlsup {\isadigit{1}}} is noted here as \isa{{\isasymkappa}\isactrlsub {\isadigit{1}}{\isasymcdot}{\isasymPi}\isactrlsup {\isadigit{1}}}. 

@@

\ Enc{\isacharcolon}{\isacharcolon}{\isachardoublequoteopen}e\ opt{\isasymRightarrow}{\isacharparenleft}e{\isasymRightarrow}io{\isacharparenright}\ opt{\isasymRightarrow}io\ opt{\isachardoublequoteclose}{\isacharparenleft}{\isachardoublequoteopen}{\isasymlbrace}{\isacharunderscore}{\isacharcomma}{\isacharunderscore}{\isasymrbrace}{\isachardoublequoteclose}{\isacharparenright}\ \isakeyword{where}\ {\isachardoublequoteopen}{\isasymlbrace}x{\isacharcomma}{\isasymPhi}{\isasymrbrace}\ {\isasymequiv}\ case\ {\isacharparenleft}x{\isacharcomma}{\isasymPhi}{\isacharparenright}\ of\ \isanewline

@@

Exemplifying formulas \isa{{\isasymPi}\isactrlsup {\isadigit{1}}{\isasymkappa}\isactrlsub {\isadigit{1}}} are noted here as \isa{{\isasymPi}\isactrlsup {\isadigit{1}}{\isasymbullet}{\isasymkappa}\isactrlsub {\isadigit{1}}}.  

@@

\ Exe{\isadigit{1}}{\isacharcolon}{\isacharcolon}{\isachardoublequoteopen}{\isacharparenleft}e{\isasymRightarrow}io{\isacharparenright}\ opt{\isasymRightarrow}e\ opt{\isasymRightarrow}io\ opt{\isachardoublequoteclose}{\isacharparenleft}{\isachardoublequoteopen}{\isasymlparr}{\isacharunderscore}{\isacharcomma}{\isacharunderscore}{\isasymrparr}{\isachardoublequoteclose}{\isacharparenright}\ \isakeyword{where}\ {\isachardoublequoteopen}{\isasymlparr}{\isasymPhi}{\isacharcomma}x{\isasymrparr}\ {\isasymequiv}\ case\ {\isacharparenleft}{\isasymPhi}{\isacharcomma}x{\isacharparenright}\ of\ \isanewline

@@

\ Exe{\isadigit{2}}{\isacharcolon}{\isacharcolon}{\isachardoublequoteopen}{\isacharparenleft}e{\isasymRightarrow}e{\isasymRightarrow}io{\isacharparenright}\ opt{\isasymRightarrow}e\ opt{\isasymRightarrow}e\ opt{\isasymRightarrow}io\ opt{\isachardoublequoteclose}{\isacharparenleft}{\isachardoublequoteopen}{\isasymlparr}{\isacharunderscore}{\isacharcomma}{\isacharunderscore}{\isacharcomma}{\isacharunderscore}{\isasymrparr}{\isachardoublequoteclose}{\isacharparenright}\ \isakeyword{where}\ {\isachardoublequoteopen}{\isasymlparr}{\isasymPhi}{\isacharcomma}x{\isadigit{1}}{\isacharcomma}x{\isadigit{2}}{\isasymrparr}\ {\isasymequiv}\ case\ {\isacharparenleft}{\isasymPhi}{\isacharcomma}x{\isadigit{1}}{\isacharcomma}x{\isadigit{2}}{\isacharparenright}\ of\ \isanewline

@@

\ Exe{\isadigit{3}}{\isacharcolon}{\isacharcolon}{\isachardoublequoteopen}{\isacharparenleft}e{\isasymRightarrow}e{\isasymRightarrow}e{\isasymRightarrow}io{\isacharparenright}\ opt{\isasymRightarrow}e\ opt{\isasymRightarrow}e\ opt{\isasymRightarrow}e\ opt{\isasymRightarrow}io\ opt{\isachardoublequoteclose}{\isacharparenleft}{\isachardoublequoteopen}{\isasymlparr}{\isacharunderscore}{\isacharcomma}{\isacharunderscore}{\isacharcomma}{\isacharunderscore}{\isacharcomma}{\isacharunderscore}{\isasymrparr}{\isachardoublequoteclose}{\isacharparenright}\ \ \isakeyword{where}\ {\isachardoublequoteopen}{\isasymlparr}{\isasymPhi}{\isacharcomma}x{\isadigit{1}}{\isacharcomma}x{\isadigit{2}}{\isacharcomma}x{\isadigit{3}}{\isasymrparr}\ {\isasymequiv}\ case\ {\isacharparenleft}{\isasymPhi}{\isacharcomma}x{\isadigit{1}}{\isacharcomma}x{\isadigit{2}}{\isacharcomma}x{\isadigit{3}}{\isacharparenright}\ of\ \isanewline

@@

\ not{\isacharcolon}{\isacharcolon}{\isachardoublequoteopen}io\ opt{\isasymRightarrow}io\ opt{\isachardoublequoteclose}{\isacharparenleft}{\isachardoublequoteopen}\isactrlbold {\isasymnot}{\isachardoublequoteclose}{\isacharparenright}\ \isakeyword{where}\ {\isachardoublequoteopen}\isactrlbold {\isasymnot}\ {\isasymphi}\ {\isasymequiv}\ case\ {\isasymphi}\ of\ \isanewline

@@

\ implies{\isacharcolon}{\isacharcolon}{\isachardoublequoteopen}io\ opt{\isasymRightarrow}io\ opt{\isasymRightarrow}io\ opt{\isachardoublequoteclose}{\isacharparenleft}\isakeyword{infixl}\ {\isachardoublequoteopen}\isactrlbold {\isasymrightarrow}{\isachardoublequoteclose}\ {\isadigit{5}}{\isadigit{1}}{\isacharparenright}\ \isakeyword{where}\ {\isachardoublequoteopen}{\isasymphi}\ \isactrlbold {\isasymrightarrow}\ {\isasympsi}\ {\isasymequiv}\ case\ {\isacharparenleft}{\isasymphi}{\isacharcomma}{\isasympsi}{\isacharparenright}\ of\ \isanewline

@@

\ forall{\isacharcolon}{\isacharcolon}{\isachardoublequoteopen}{\isacharparenleft}{\isacharprime}a{\isasymRightarrow}io\ opt{\isacharparenright}{\isasymRightarrow}io\ opt{\isachardoublequoteclose}{\isacharparenleft}{\isachardoublequoteopen}\isactrlbold {\isasymforall}{\isachardoublequoteclose}{\isacharparenright}\ \isakeyword{where}\ {\isachardoublequoteopen}\isactrlbold {\isasymforall}\ {\isasymPhi}\ {\isasymequiv}\ case\ {\isacharparenleft}{\isasymPhi}\ da{\isacharparenright}\ of\isanewline

@@

\ forallBinder{\isacharcolon}{\isacharcolon}{\isachardoublequoteopen}{\isacharparenleft}{\isacharprime}a{\isasymRightarrow}io\ opt{\isacharparenright}{\isasymRightarrow}io\ opt{\isachardoublequoteclose}\ {\isacharparenleft}\isakeyword{binder}\ {\isachardoublequoteopen}\isactrlbold {\isasymforall}{\isachardoublequoteclose}\ {\isacharbrackleft}{\isadigit{9}}{\isacharbrackright}\ {\isadigit{9}}{\isacharparenright}\ \ \isakeyword{where}\ {\isachardoublequoteopen}\isactrlbold {\isasymforall}\ x{\isachardot}\ {\isasymphi}\ x\ {\isasymequiv}\ \isactrlbold {\isasymforall}\ {\isasymphi}{\isachardoublequoteclose}\isanewline

@@

\ box{\isacharcolon}{\isacharcolon}{\isachardoublequoteopen}io\ opt{\isasymRightarrow}io\ opt{\isachardoublequoteclose}{\isacharparenleft}{\isachardoublequoteopen}\isactrlbold {\isasymbox}{\isachardoublequoteclose}{\isacharparenright}\ \isakeyword{where}\ {\isachardoublequoteopen}\isactrlbold {\isasymbox}{\isasymphi}\ {\isasymequiv}\ case\ {\isasymphi}\ of\ \isanewline

@@

 For pragmatical reasons we restrict ourselves here to the cases where $n\leq 0$.%
\ lam{\isadigit{0}}{\isacharcolon}{\isacharcolon}{\isachardoublequoteopen}io\ opt{\isasymRightarrow}io\ opt{\isachardoublequoteclose}{\isacharparenleft}{\isachardoublequoteopen}\isactrlbold {\isasymlambda}\isactrlsup {\isadigit{0}}{\isachardoublequoteclose}{\isacharparenright}\ \isakeyword{where}\ {\isachardoublequoteopen}\isactrlbold {\isasymlambda}\isactrlsup {\isadigit{0}}{\isasymphi}\ {\isasymequiv}\ case\ {\isasymphi}\ of\ \isanewline

@@

\ lam{\isacharcolon}{\isacharcolon}{\isachardoublequoteopen}{\isacharparenleft}e{\isasymRightarrow}io\ opt{\isacharparenright}{\isasymRightarrow}{\isacharparenleft}e{\isasymRightarrow}io{\isacharparenright}\ opt{\isachardoublequoteclose}{\isacharparenleft}{\isachardoublequoteopen}\isactrlbold {\isasymlambda}{\isachardoublequoteclose}{\isacharparenright}\ \isakeyword{where}\ {\isachardoublequoteopen}\isactrlbold {\isasymlambda}{\isasymPhi}\ {\isasymequiv}\ case\ {\isacharparenleft}{\isasymPhi}\ de{\isacharparenright}\ of\isanewline

@@

\ lam{\isadigit{1}}Binder{\isacharcolon}{\isacharcolon}{\isachardoublequoteopen}{\isacharparenleft}e{\isasymRightarrow}io\ opt{\isacharparenright}{\isasymRightarrow}{\isacharparenleft}e{\isasymRightarrow}io{\isacharparenright}\ opt{\isachardoublequoteclose}\ {\isacharparenleft}\isakeyword{binder}\ {\isachardoublequoteopen}\isactrlbold {\isasymlambda}{\isachardoublequoteclose}\ {\isacharbrackleft}{\isadigit{9}}{\isacharbrackright}\ {\isadigit{9}}{\isacharparenright}\ \ \isakeyword{where}\ {\isachardoublequoteopen}\isactrlbold {\isasymlambda}\ x{\isachardot}\ {\isasymphi}\ x\ {\isasymequiv}\ \isactrlbold {\isasymlambda}\ {\isasymphi}{\isachardoublequoteclose}\isanewline
\ lam{\isadigit{2}}{\isacharcolon}{\isacharcolon}{\isachardoublequoteopen}{\isacharparenleft}e{\isasymRightarrow}e{\isasymRightarrow}io\ opt{\isacharparenright}{\isasymRightarrow}{\isacharparenleft}e{\isasymRightarrow}e{\isasymRightarrow}io{\isacharparenright}\ opt{\isachardoublequoteclose}{\isacharparenleft}{\isachardoublequoteopen}\isactrlbold {\isasymlambda}\isactrlsup {\isadigit{2}}{\isachardoublequoteclose}{\isacharparenright}\ \isakeyword{where}\ {\isachardoublequoteopen}\isactrlbold {\isasymlambda}\isactrlsup {\isadigit{2}}{\isasymPhi}\ {\isasymequiv}\ case\ {\isacharparenleft}{\isasymPhi}\ de\ de{\isacharparenright}\ of\isanewline

@@

 reported (for dummy entity \isa{de}).%
\ that{\isacharcolon}{\isacharcolon}{\isachardoublequoteopen}{\isacharparenleft}e{\isasymRightarrow}io\ opt{\isacharparenright}{\isasymRightarrow}e\ opt{\isachardoublequoteclose}{\isacharparenleft}{\isachardoublequoteopen}{\isasymiota}{\isachardoublequoteclose}{\isacharparenright}\ \ \isakeyword{where}\ {\isachardoublequoteopen}{\isasymiota}\ {\isasymPhi}\ {\isasymequiv}\ case\ {\isacharparenleft}{\isasymPhi}\ de{\isacharparenright}\ of\isanewline

>>>>

 The motivating research questions for the work presented below include:
 \begin{itemize} 
 \item Can functional type theory, despite the problems as pointed by Zalta and Oppenheimer, 
  be utilized to encode the Theory of Abstract Objects when following the embeddings approach?
 \item How elegant and user-friendly is the resulting formalization? In other
  words, to what extend can Isabelle's  user interface be facilitated to hide 
  unpleasant technicalities of the (extended) embedding from the user?
 \item How far can automation be pushed in the approach? How much user interaction can
  be avoided in the formalization of the (first part) of the Principia Metaphysica? 
 \item Can the consistency of the theory be validated with the available automated 
  reasoning tools?
 \item Can the reasoners eventually even contribute some new knowledge? 
 \ldots
 \end{itemize}%
\end{isamarkuptext}%
\isamarkuptrue%
%
\begin{isamarkuptext}%
The encoding of modal functional type theory in functional type theory as explored in 
 previous work \cite{J23,C40} is simple: modal logic formulas are identified with certain functional 
 type theory formulas of predicate type \isa{i{\isasymRightarrow}bool} (abbreviated as \isa{io} below). 
 Possible worlds are explicitly represented by 
 terms of type  \isa{i}. A modal logic \isa{{\isasymphi}} formula holds for a world \isa{w} if and 
 only if the application \isa{{\isasymphi}\ w} evaluates to true. The definition of the propositional modal logic 
 connectives is then straightforward and it simply realizes the standard translation as a set of equations 
 in functional type theory. The approach has been successfully extended for quantifiers. A crucial 
 aspect thereby is that in simple type theory quantifiers can be treated
 as ordinary logical connectives. No extra binding mechanism is needed since the already existing 
 lambda binding mechanism can be elegantly utilized.

 The challenge here is to appropriately 'restrict' this embedding for modal relational type theory.
  \begin{figure}[t]
 \includegraphics[height=5.5cm]{ModalRelationalTypeTheory.png}\includegraphics[height=4.5cm]{ModalRelationalTypeTheory2.png}
 \caption{Grammar of Modal Relational Type Theory. \label{mmrt}
 Note that two kinds of (complex) formulas are introduced: ones that may have encoding subformulas and ones that don’t.
 The latter are designated as propositional formulas, the former ones simply as formulas. }
 \end{figure}

@@

 Our formalism explicitly encodes possible world semantics. Hence, we introduce a 

@@

 (polymorphic) datatype \isa{{\isacharprime}a\ opt} (where \isa{{\isacharprime}a} is a polymorphic variable in Isabelle) 
 based on four constructors: \isa{ERR\ {\isacharprime}a} (identifies erroneous term constructions), \isa{P\ {\isacharprime}a} (identifies 

@@

\ mkP{\isacharcolon}{\isacharcolon}{\isachardoublequoteopen}io{\isasymRightarrow}io\ opt{\isachardoublequoteclose}\ {\isacharparenleft}{\isachardoublequoteopen}{\isacharunderscore}\isactrlsup P{\isachardoublequoteclose}\ {\isacharbrackleft}{\isadigit{1}}{\isadigit{0}}{\isadigit{9}}{\isacharbrackright}\ {\isadigit{1}}{\isadigit{1}}{\isadigit{0}}{\isacharparenright}\ \ \isakeyword{where}\ {\isachardoublequoteopen}{\isasymphi}\isactrlsup P\ {\isasymequiv}\ P\ {\isasymphi}{\isachardoublequoteclose}\ \isanewline
\ mkF{\isacharcolon}{\isacharcolon}{\isachardoublequoteopen}io{\isasymRightarrow}io\ opt{\isachardoublequoteclose}\ {\isacharparenleft}{\isachardoublequoteopen}{\isacharunderscore}\isactrlsup F{\isachardoublequoteclose}\ {\isacharbrackleft}{\isadigit{1}}{\isadigit{0}}{\isadigit{9}}{\isacharbrackright}\ {\isadigit{1}}{\isadigit{1}}{\isadigit{0}}{\isacharparenright}\ \ \isakeyword{where}\ {\isachardoublequoteopen}{\isasymphi}\isactrlsup F\ {\isasymequiv}\ F\ {\isasymphi}{\isachardoublequoteclose}\ \isanewline
\ mkT{\isacharcolon}{\isacharcolon}{\isachardoublequoteopen}{\isacharprime}a{\isasymRightarrow}{\isacharprime}a\ opt{\isachardoublequoteclose}\ {\isacharparenleft}{\isachardoublequoteopen}{\isacharunderscore}\isactrlsup T{\isachardoublequoteclose}\ {\isacharbrackleft}{\isadigit{1}}{\isadigit{0}}{\isadigit{9}}{\isacharbrackright}\ {\isadigit{1}}{\isadigit{1}}{\isadigit{0}}{\isacharparenright}\ \ \isakeyword{where}\ {\isachardoublequoteopen}{\isasymphi}\isactrlsup T\ {\isasymequiv}\ T\ {\isasymphi}{\isachardoublequoteclose}\isanewline
\ mkE{\isacharcolon}{\isacharcolon}{\isachardoublequoteopen}{\isacharprime}a{\isasymRightarrow}{\isacharprime}a\ opt{\isachardoublequoteclose}\ {\isacharparenleft}{\isachardoublequoteopen}{\isacharunderscore}\isactrlsup E{\isachardoublequoteclose}\ {\isacharbrackleft}{\isadigit{1}}{\isadigit{0}}{\isadigit{9}}{\isacharbrackright}\ {\isadigit{1}}{\isadigit{1}}{\isadigit{0}}{\isacharparenright}\ \ \isakeyword{where}\ {\isachardoublequoteopen}{\isasymphi}\isactrlsup E\ {\isasymequiv}\ ERR\ {\isasymphi}{\isachardoublequoteclose}%

@@

 \isa{ERR} (error) or \isa{T} (term), then the syntactical catagory of \isa{{\isasymA}\ {\isasymphi}} 
 is \isa{ERR} and a dummy entity of appropriate type is returned. This illustrates the very 

@@

 Encoding \isa{{\isasymkappa}\isactrlsub {\isadigit{1}}{\isasymPi}\isactrlsup {\isadigit{1}}} is noted here as \isa{{\isasymlbrace}{\isasymkappa}\isactrlsub {\isadigit{1}}{\isacharcomma}{\isasymPi}\isactrlsup {\isadigit{1}}{\isasymrbrace}}. 

@@

\ Enc{\isacharcolon}{\isacharcolon}{\isachardoublequoteopen}e\ opt{\isasymRightarrow}{\isacharparenleft}e{\isasymRightarrow}io{\isacharparenright}\ opt{\isasymRightarrow}io\ opt{\isachardoublequoteclose}\ {\isacharparenleft}{\isachardoublequoteopen}{\isasymlbrace}{\isacharunderscore}{\isacharcomma}{\isacharunderscore}{\isasymrbrace}{\isachardoublequoteclose}{\isacharparenright}\ \isakeyword{where}\ {\isachardoublequoteopen}{\isasymlbrace}x{\isacharcomma}{\isasymPhi}{\isasymrbrace}\ {\isasymequiv}\ case\ {\isacharparenleft}x{\isacharcomma}{\isasymPhi}{\isacharparenright}\ of\ \isanewline

@@

Exemplifying formulas \isa{{\isasymPi}\isactrlsup {\isadigit{1}}{\isasymkappa}\isactrlsub {\isadigit{1}}} are noted here as \isa{{\isasymlparr}{\isasymPi}\isactrlsup {\isadigit{1}}{\isacharcomma}{\isasymkappa}\isactrlsub {\isadigit{1}}{\isasymrparr}}.  

@@

\ Exe{\isadigit{1}}{\isacharcolon}{\isacharcolon}{\isachardoublequoteopen}{\isacharparenleft}e{\isasymRightarrow}io{\isacharparenright}\ opt{\isasymRightarrow}e\ opt{\isasymRightarrow}io\ opt{\isachardoublequoteclose}\ {\isacharparenleft}{\isachardoublequoteopen}{\isasymlparr}{\isacharunderscore}{\isacharcomma}{\isacharunderscore}{\isasymrparr}{\isachardoublequoteclose}{\isacharparenright}\ \isakeyword{where}\ {\isachardoublequoteopen}{\isasymlparr}{\isasymPhi}{\isacharcomma}x{\isasymrparr}\ {\isasymequiv}\ case\ {\isacharparenleft}{\isasymPhi}{\isacharcomma}x{\isacharparenright}\ of\ \isanewline

@@

\ Exe{\isadigit{2}}{\isacharcolon}{\isacharcolon}{\isachardoublequoteopen}{\isacharparenleft}e{\isasymRightarrow}e{\isasymRightarrow}io{\isacharparenright}\ opt{\isasymRightarrow}e\ opt{\isasymRightarrow}e\ opt{\isasymRightarrow}io\ opt{\isachardoublequoteclose}\ {\isacharparenleft}{\isachardoublequoteopen}{\isasymlparr}{\isacharunderscore}{\isacharcomma}{\isacharunderscore}{\isacharcomma}{\isacharunderscore}{\isasymrparr}{\isachardoublequoteclose}{\isacharparenright}\ \isakeyword{where}\ {\isachardoublequoteopen}{\isasymlparr}{\isasymPhi}{\isacharcomma}x{\isadigit{1}}{\isacharcomma}x{\isadigit{2}}{\isasymrparr}\ {\isasymequiv}\ case\ {\isacharparenleft}{\isasymPhi}{\isacharcomma}x{\isadigit{1}}{\isacharcomma}x{\isadigit{2}}{\isacharparenright}\ of\ \isanewline

@@

\ Exe{\isadigit{3}}{\isacharcolon}{\isacharcolon}{\isachardoublequoteopen}{\isacharparenleft}e{\isasymRightarrow}e{\isasymRightarrow}e{\isasymRightarrow}io{\isacharparenright}\ opt{\isasymRightarrow}e\ opt{\isasymRightarrow}e\ opt{\isasymRightarrow}e\ opt{\isasymRightarrow}io\ opt{\isachardoublequoteclose}\ {\isacharparenleft}{\isachardoublequoteopen}{\isasymlparr}{\isacharunderscore}{\isacharcomma}{\isacharunderscore}{\isacharcomma}{\isacharunderscore}{\isacharcomma}{\isacharunderscore}{\isasymrparr}{\isachardoublequoteclose}{\isacharparenright}\ \ \isakeyword{where}\ {\isachardoublequoteopen}{\isasymlparr}{\isasymPhi}{\isacharcomma}x{\isadigit{1}}{\isacharcomma}x{\isadigit{2}}{\isacharcomma}x{\isadigit{3}}{\isasymrparr}\ {\isasymequiv}\ case\ {\isacharparenleft}{\isasymPhi}{\isacharcomma}x{\isadigit{1}}{\isacharcomma}x{\isadigit{2}}{\isacharcomma}x{\isadigit{3}}{\isacharparenright}\ of\ \isanewline

@@

\ not{\isacharcolon}{\isacharcolon}{\isachardoublequoteopen}io\ opt{\isasymRightarrow}io\ opt{\isachardoublequoteclose}\ \ {\isacharparenleft}{\isachardoublequoteopen}\isactrlbold {\isasymnot}\ {\isacharunderscore}{\isachardoublequoteclose}\ {\isacharbrackleft}{\isadigit{5}}{\isadigit{8}}{\isacharbrackright}\ {\isadigit{5}}{\isadigit{9}}{\isacharparenright}\ \isakeyword{where}\ {\isachardoublequoteopen}\isactrlbold {\isasymnot}\ {\isasymphi}\ {\isasymequiv}\ case\ {\isasymphi}\ of\ \isanewline

@@

\ implies{\isacharcolon}{\isacharcolon}{\isachardoublequoteopen}io\ opt{\isasymRightarrow}io\ opt{\isasymRightarrow}io\ opt{\isachardoublequoteclose}\ {\isacharparenleft}\isakeyword{infixl}\ {\isachardoublequoteopen}\isactrlbold {\isasymrightarrow}{\isachardoublequoteclose}\ {\isadigit{5}}{\isadigit{1}}{\isacharparenright}\ \isakeyword{where}\ {\isachardoublequoteopen}{\isasymphi}\ \isactrlbold {\isasymrightarrow}\ {\isasympsi}\ {\isasymequiv}\ case\ {\isacharparenleft}{\isasymphi}{\isacharcomma}{\isasympsi}{\isacharparenright}\ of\ \isanewline

@@

\ forall{\isacharcolon}{\isacharcolon}{\isachardoublequoteopen}{\isacharparenleft}{\isacharprime}a{\isasymRightarrow}io\ opt{\isacharparenright}{\isasymRightarrow}io\ opt{\isachardoublequoteclose}\ {\isacharparenleft}{\isachardoublequoteopen}\isactrlbold {\isasymforall}{\isachardoublequoteclose}{\isacharparenright}\ \isakeyword{where}\ {\isachardoublequoteopen}\isactrlbold {\isasymforall}\ {\isasymPhi}\ {\isasymequiv}\ case\ {\isacharparenleft}{\isasymPhi}\ da{\isacharparenright}\ of\isanewline

@@

\ forallBinder{\isacharcolon}{\isacharcolon}{\isachardoublequoteopen}{\isacharparenleft}{\isacharprime}a{\isasymRightarrow}io\ opt{\isacharparenright}{\isasymRightarrow}io\ opt{\isachardoublequoteclose}\ {\isacharparenleft}\isakeyword{binder}\ {\isachardoublequoteopen}\isactrlbold {\isasymforall}{\isachardoublequoteclose}\ {\isacharbrackleft}{\isadigit{8}}{\isacharbrackright}\ {\isadigit{9}}{\isacharparenright}\ \ \isakeyword{where}\ {\isachardoublequoteopen}\isactrlbold {\isasymforall}\ x{\isachardot}\ {\isasymphi}\ x\ {\isasymequiv}\ \isactrlbold {\isasymforall}\ {\isasymphi}{\isachardoublequoteclose}\isanewline

@@

\ box{\isacharcolon}{\isacharcolon}{\isachardoublequoteopen}io\ opt{\isasymRightarrow}io\ opt{\isachardoublequoteclose}\ {\isacharparenleft}{\isachardoublequoteopen}\isactrlbold {\isasymbox}\ {\isacharunderscore}{\isachardoublequoteclose}\ {\isacharbrackleft}{\isadigit{6}}{\isadigit{2}}{\isacharbrackright}\ {\isadigit{6}}{\isadigit{3}}{\isacharparenright}\ \isakeyword{where}\ {\isachardoublequoteopen}\isactrlbold {\isasymbox}{\isasymphi}\ {\isasymequiv}\ case\ {\isasymphi}\ of\ \isanewline

@@

 For pragmatical reasons we restrict ourselves here to the cases where $n\leq 0$. Binder notation is
 introduced for \isa{\isactrlbold {\isasymlambda}} (... unfortuntaley, I don't know yet how this can be achieved as well 
 for \isa{\isactrlbold {\isasymlambda}\isactrlsup {\isadigit{2}}{\isacharcomma}\isactrlbold {\isasymlambda}\isactrlsup {\isadigit{3}}{\isacharcomma}{\isachardot}{\isachardot}{\isachardot}} ...)%
\ lam{\isadigit{0}}{\isacharcolon}{\isacharcolon}{\isachardoublequoteopen}io\ opt{\isasymRightarrow}io\ opt{\isachardoublequoteclose}\ {\isacharparenleft}{\isachardoublequoteopen}\isactrlbold {\isasymlambda}\isactrlsup {\isadigit{0}}{\isachardoublequoteclose}{\isacharparenright}\ \isakeyword{where}\ {\isachardoublequoteopen}\isactrlbold {\isasymlambda}\isactrlsup {\isadigit{0}}{\isasymphi}\ {\isasymequiv}\ case\ {\isasymphi}\ of\ \isanewline

@@

\ lam{\isacharcolon}{\isacharcolon}{\isachardoublequoteopen}{\isacharparenleft}e{\isasymRightarrow}io\ opt{\isacharparenright}{\isasymRightarrow}{\isacharparenleft}e{\isasymRightarrow}io{\isacharparenright}\ opt{\isachardoublequoteclose}\ {\isacharparenleft}{\isachardoublequoteopen}\isactrlbold {\isasymlambda}{\isachardoublequoteclose}{\isacharparenright}\ \isakeyword{where}\ {\isachardoublequoteopen}\isactrlbold {\isasymlambda}{\isasymPhi}\ {\isasymequiv}\ case\ {\isacharparenleft}{\isasymPhi}\ de{\isacharparenright}\ of\isanewline

@@

\ lamBinder{\isacharcolon}{\isacharcolon}{\isachardoublequoteopen}{\isacharparenleft}e{\isasymRightarrow}io\ opt{\isacharparenright}{\isasymRightarrow}{\isacharparenleft}e{\isasymRightarrow}io{\isacharparenright}\ opt{\isachardoublequoteclose}\ {\isacharparenleft}\isakeyword{binder}\ {\isachardoublequoteopen}\isactrlbold {\isasymlambda}{\isachardoublequoteclose}\ {\isacharbrackleft}{\isadigit{8}}{\isacharbrackright}\ {\isadigit{9}}{\isacharparenright}\ \ \isakeyword{where}\ {\isachardoublequoteopen}\isactrlbold {\isasymlambda}\ x{\isachardot}\ {\isasymphi}\ x\ {\isasymequiv}\ \isactrlbold {\isasymlambda}\ {\isasymphi}{\isachardoublequoteclose}\isanewline
\ lam{\isadigit{2}}{\isacharcolon}{\isacharcolon}{\isachardoublequoteopen}{\isacharparenleft}e{\isasymRightarrow}e{\isasymRightarrow}io\ opt{\isacharparenright}{\isasymRightarrow}{\isacharparenleft}e{\isasymRightarrow}e{\isasymRightarrow}io{\isacharparenright}\ opt{\isachardoublequoteclose}\ {\isacharparenleft}{\isachardoublequoteopen}\isactrlbold {\isasymlambda}\isactrlsup {\isadigit{2}}{\isachardoublequoteclose}{\isacharparenright}\ \isakeyword{where}\ {\isachardoublequoteopen}\isactrlbold {\isasymlambda}\isactrlsup {\isadigit{2}}{\isasymPhi}\ {\isasymequiv}\ case\ {\isacharparenleft}{\isasymPhi}\ de\ de{\isacharparenright}\ of\isanewline

@@

 reported (for dummy entity \isa{de}). We again introduce binder notation.%
\ that{\isacharcolon}{\isacharcolon}{\isachardoublequoteopen}{\isacharparenleft}e{\isasymRightarrow}io\ opt{\isacharparenright}{\isasymRightarrow}e\ opt{\isachardoublequoteclose}\ {\isacharparenleft}{\isachardoublequoteopen}{\isasymiota}{\isachardoublequoteclose}{\isacharparenright}\ \ \isakeyword{where}\ {\isachardoublequoteopen}{\isasymiota}\ {\isasymPhi}\ {\isasymequiv}\ case\ {\isacharparenleft}{\isasymPhi}\ de{\isacharparenright}\ of\isanewline
